### 2021-06-14 project_rodolfo/paper.tex
rodolfo

\def\Student{Ashish Sehrawat}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}

%%header and footer
\lhead{\Student\ / \ \Dept}
\rhead{\Title}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

@@

%%%%Title Page
\begin{titlepage}
\centering
\hspace{0pt}
\vfill
{\scshape\Large \Title \par}
project revised 2021-1

  \vspace{2cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle \par}
  }

  \vspace{0.5cm}
  {
    RESEARCH LINE: \par
    \ResearchLine \par
  }

  \vspace{4cm}
  {\underline{\hspace{8cm}}\par}
  {\bf \scshape \Student \par}
  {Student\par}

@@

  \vspace{4cm}
  {\today}

@@

  This research project proposes to determine precise value and corresponding uncertainity of luminosity delivered to Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period using Pixel Cluster Counting (PCC) method and construction of luminosity measurement device using Tracker Endcap Pixel Detector (TEPX) for High Luminosity (HL)-LHC which will be able to withstand luminosities of up to 3000 $fb^{-1}$. Luminosity plays a vital role in determination of cross section for various production and decay processes of elementary particles and its accurate determination will assist in precise calculation of SM quantities like cross section, couplings and exploring physics beyond SM.

  \hspace{2pt}
\vfill

@@

The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase}\cite{Collaboration:2706512}.

@@

This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).

@@

The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX). TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).

@@

For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components. 
However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.

@@

\par
For the development of the HL-LHC upgrade system:
\begin{itemize}
\item study the different parts of the TEPX detector.
\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds.
\item determine the linearity and statistical precision of the PCC method and coincidence counting method for the TEPX detector and its constituent parts (disks and rings).
\end{itemize}

@@

For the upgrade part of this project, the research consists of studying the expected performance of the TEPX disks of the CMS tracker in the HL-LHC phase.
The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>170$ cm. In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk.
Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
The linearity of the cluster counting algorithm will be studied.
In addition, a new algorithm will be developed to detect cluster coincidences between consecutive layers of a disk.
It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
  \label{fig:CMS}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./TEPX_rz.pdf}
  \includegraphics[width=0.27\columnwidth]{./TEPX_rphi.pdf}
  \caption{
    Left: Longitudial view of the current design of the CMS tracker detector for the HL-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|>$ 1700 mm.
    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings \cite{Klein:2017nke}.
  }
  \label{fig:tepx}
\end{figure}

@@

From this project two main publications are expected:
\begin{itemize}
\item
For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
The results of these studies will be published in a peer-reviewed scientific journal.
\item
For the development of the HL-LHC upgrade system, we expect to produce a Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector. This document will be published in the CERN document server (CDS) and submitted to the LHC committee for approval of required funding for the construction and operation of the system.
\end{itemize}

@@

\item {\bf Semester 1 (2019-2)}:
  \SubItem{ Readings on Standard Model of particle physics theory}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Initial planning of the analysis strategy}

\item {\bf Semester 2 (2020-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis}
  \SubItem{ Readings on the LHC and CMS experiments}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 3 (2020-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 4 (2021-1)}:
  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
  \SubItem{ Writing of the monograph}

\item {\bf Semester 5 (2021-2)}:
  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}

\item {\bf Semester 6 (2022-1)}:
  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}

\item {\bf Semester 7 (2022-2)}:
  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}

\item {\bf Semester 8 (2023-1)}: 
  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
  \SubItem{ Writing of the Ph.D thesis}

>>>>

\def\Student{Jesus Rodolfo MORENO CHAVEZ }
\def\Title{MASTERS THESIS PROJECT}
\def\TitleESP{(ANTEPROYECTO)}
\def\Prog{Maestria en Ciencias (F\'{i}sica) }
%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Dept{DIFUS}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Measurement of the Large Hadron Collider luminosity using the CMS silicon pixel detector}
\def\ProjectTitleESP{Medic\'{i}on de la luminosidad del Gran Colisionador de Hadrones usando el detector de pixeles de silicio de CMS}
\def\ResearchLine{Fisica Matematica}

%%header and footer
\lhead{\Student\ / \ \Dept}
\rhead{\TitleESP}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

@@

%%%%Title Page
\begin{titlepage}
\centering
\hspace{0pt}
%\vfill
{\scshape\Large \Title \\ \TitleESP \par}
%%project revised 2021-1

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}
    \\
    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

  \vspace{1cm}
  {
    RESEARCH LINE (LGAC): \par
    \ResearchLine \par
  }

  \vspace{2cm}
  {\underline{\hspace{8cm}}\par}
  {\bf \scshape \Student \par}
  {Student\par}

@@

  \vspace{2cm}
  {\today}

@@

  This research project consists on the precise determination of the luminosity delivered by the Large Hadron Collider to the Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period  using the Pixel Cluster Counting (PCC) method.
  Luminosity plays a fundamental role in the  measurement of physics processes of elementary particles of the Standard Model, a precise determination of the delivered luminosity allows for precise tests of the Standard Model and searches for new physics.
The PCC method consists of the reconstruction and counting of track clusters produced by charged particle tracks using the Inner Tracker of the CMS detector.
Due to the fine granularity of the pixel sensors of the Inner Tracker, the hit occupancy in the sensors remains very small ($<1\%$) during the proton collisions, this leads to a very linear response and small overall systematic uncertainties for the luminosity measurement.   
  \hspace{2pt}
\vfill

@@

The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
%In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase\cite{Collaboration:2706512}.

@@

In the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.

@@

%The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX). TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).

@@

%For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components. 
%However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.

@@

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./cms_layers.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
  \label{fig:CMS}
\end{figure}

@@

@@

For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
The results of these studies will be published in a peer-reviewed scientific journal.

@@

\item {\bf Summer 2021}:
  \SubItem{ Readings on Standard Model of particle physics theory}
  \SubItem{ Readings on the LHC and CMS experiments}
  \SubItem{ Linux/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ Initial planning of the analysis strategy}

\item {\bf Semester 2021-2}:
  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
  \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
  \SubItem{ Analysis of the LHC Run 2 data using the PCC method}

\item {\bf Semester 2022-1}:
  \SubItem{ Completion of the analysis of the LHC Run 2 data using the PCC method}
  \SubItem{ Presentation of results at national or international conference}
  \SubItem{ Thesis writing}
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
